Title page

### 2024-09-04 output/Title_page.Rmd
Moves Statements and Declarations to title page
Corrects formatting issues

---
title: "Title page"
output:
  officedown::rdocx_document:
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
editor_options: 
  chunk_output_type: console
---

@@

Daniel Morillo-Cuadrado \\
Faculty of Psychology, Office 2.74.
C. de Juan del Rosal 10, 28040 Madrid

Phone nº: +34 91398 6584
Email address: dvmorillo@psi.uned.es

>>>>

---
output:
  officedown::rdocx_document:
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
editor_options: 
  chunk_output_type: console
---

@@

Daniel Morillo-Cuadrado \
Faculty of Psychology, Office 2.74.
C. de Juan del Rosal 10, 28040 Madrid

Phone nº: +34 91398 6584 \
Email address: dvmorillo@psi.uned.es

# Statements and Declarations

## Ethical considerations

Not applicable

## Consent to participate

Not applicable

## Consent for publication

Not applicable

## Declaration of conflicting interest

The author(s) declared no potential conflicts of interest with respect to
the research, authorship, and/or publication of this article.

## Funding statement

Not applicable

## Data availability statement

Not applicable
